### 2020-04-21 dataclean.tex
moved figure

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Viewing and Cleaning the Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Viewing and Cleaning the Data}
\label{section:dataclean}
\begin{figure*}[bt]
  \includegraphics[width=6.5in]{figs/sample_sn.pdf}
  \caption{Serial number view of GPU life and failures. Legend: black
    dots are installs, black lines are lifetimes at installed
    location, blue squares are OTB events, red triangles are DBE
    events, and black ] are ``last seen'' events.}
  \label{fig:gpuview}
\end{figure*}
As we need to recover durations in operation from this data, correct
processing involves time adjustments for switching between daylight
saving time and standard time and leap years. We perform this by
setting a reference time zone (Eastern time) and converting all
date-times from strings into POSIX date-time variables with the R
\pkg{lubridate} package \cite{lubridate}, which enables appropriate
date arithmetic and sensible date constructs for graphs.

>>>>

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Viewing and Cleaning the Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bt]
  \includegraphics[width=6.5in]{figs/sample_sn.pdf}
  \caption{Serial number view of GPU life and failures. Legend: black
    dots are installs, black lines are lifetimes at installed
    location, blue squares are OTB events, red triangles are DBE
    events, and black ] are ``last seen'' events.}
  \label{fig:gpuview}
\end{figure*}
\section{Viewing and Cleaning the Data}
\label{section:dataclean}
As we need to recover durations in operation from this data, correct
processing involves time adjustments for switching between daylight
saving time and standard time and leap years. We perform this by
setting a reference time zone (Eastern time) and converting all
date-times from strings into POSIX date-time variables with the R
\pkg{lubridate} package \cite{lubridate}, which enables appropriate
date arithmetic and sensible date constructs for graphs.
